Building socket-aware BPF programs

### 2018-10-29 paper/paper.tex
Fix and share API headers

\begin{filecontents*}{sk-lookup-api.c}
\import{sk-lookup-api.c}
\end{filecontents*}
\begin{filecontents*}{sk-lookup-structures.c}
\import{sk-lookup-structures.c}
\end{filecontents*}

@@

\lstinputlisting[float=*b,%
  caption={BPF API helper functions for socket lookup},%
  language=c,%
  label=lst:helper-api,%
  breaklines=true]{sk-lookup-api.c}

\lstinputlisting[float=*b,%
  caption={BPF API structures for socket lookup (Linux v4.20)},%
  language=c,%
  label=lst:helper-struct,%
  breaklines=true]{sk-lookup-structures.c}

>>>>

\begin{filecontents*}{../sk-lookup-api.h}
\import{../sk-lookup-api.h}
\end{filecontents*}
\begin{filecontents*}{sk-lookup-structures.h}
\import{sk-lookup-structures.h}
\end{filecontents*}

@@

\lstinputlisting[float=*b,%
  caption={BPF API helper functions for socket lookup},%
  language=c,%
  label=lst:helper-api,%
  breaklines=true]{../sk-lookup-api.h}

\lstinputlisting[float=*b,%
  caption={BPF API structures for socket lookup (Linux v4.20)},%
  language=c,%
  label=lst:helper-struct,%
  breaklines=true]{sk-lookup-structures.h}
